### 2014-11-07 docs/ms.Rmd
Update ms.Rmd
Added a bit more analysis
brought back two last paragaraphs in ms.Rmd. #188da13

#The transparency of colour reporting in plant and animal taxa

@@

Analysis varied across studies but, overall `r analysisType[1]` analyzed their data by generating colormetric (brightness, hue, chroma) variables whereas `r analysisType[4]` used visual models, `r analysisType[2]` used multiple analysis types (e.g. visual model and colourmetric) and `r analysisType[3]` did other forms of analysis (e.g. RGB, PCA's, GLMMs etc.). Of the studies quantifying colour using spectral reflectance curves `r analysisTypeSpec[1]` used colormetric measures, `r analysisTypeSpec[2]` used multiple analyses, `r analysisTypeSpec[4]` used visual models and `r analysisTypeSpec[3]` used other forms of analysis.

>>>>

#The transparency of methods-reporting in studies measuring biological colouration

@@

Analysis varied across studies but, overall `r analysisType[1]` analyzed their data by generating colormetric (brightness, hue, chroma) variables whereas `r analysisType[4]` used visual models, `r analysisType[2]` used multiple analysis types (e.g. visual model and colourmetric) and `r analysisType[3]` did other forms of analysis (e.g. RGB, PCA's, GLMMs etc.). Of the studies quantifying colour using spectral reflectance curves `r analysisTypeSpec[1]` used colormetric measures, `r analysisTypeSpec[2]` used multiple analyses, `r analysisTypeSpec[4]` used visual models and `r analysisTypeSpec[3]` used other forms of analysis. Studies using colormetric measurements defined their measure of brightness, hue and/or chroma in `r round(col_def, digits = 2)`% of the studies. Of the studies analysing their data using visual models, `r round(prop_vismod, digits = 2)`% reported the type of visual model they used while only `r round(prop_irrad, digits =2)`%  reported the type of irradiance, `r round(prop_spvismod, digits = 2)`% reported the species used in their visual model and `r round(propvis_mod_param, digits = 2)`% made explicit mention of the parameters they used (i.e. cone densities, neural vs quantum catchs etc.) in their methods.
